### 2011-09-08 doc/theses/mikula/analysis_of_recent_approaches.tex
Master thesis: Corrections.

\subsection{SchemaMiner}
The SchemaMiner system \todo{bibref} is another example of a \emph{heuristic} \emph{merging state algorithm} creating the result in XSD. It focuses on inferring elements with the same name but different structure and unordered sequences.is another example of a \emph{heuristic} \emph{merging state algorithm} creating the result in XSD. It focuses on inferring elements with the same name but different structure and unordered sequences.

@@

\section{Discovering XML Keys and Foreign Keys in Queries}
This method is described in paper \cite{Necasky:2009:DXK:1529282.1529414}. It tries to improve automatic XML schema inference by discovering keys and foreign keys from a set of XQuery queries. Just these queries are utilized in inference, no XML data are used. The output of this method is a set of keys and foreign keys that can be captured using XML Schema \textbf{key}, \textbf{keyref} \todo{aj unique?} constructs.

@@

\subsubsection{Join patterns}
For a certain join, the decision for one of the cases (O1) and (O2) is made by the form of the join. The query is searched for so-called \emph{join patters}. These are \texttt{for} \emph{join pattern} and \texttt{let} \emph{join pattern} and they look as follow (the first is \texttt{for} \emph{join pattern}, the second is \texttt{let} \emph{join pattern}):

@@

@@

>>>>

\subsection{SchemaMiner}
The SchemaMiner system \todo{bibref} is another example of a \emph{heuristic} \emph{merging state algorithm} creating the result in XSD. It focuses on inferring elements with the same name but different structure and unordered sequences.is another example of a \emph{heuristic} \emph{merging state algorithm} creating the result in XSD. It focuses on inferring elements with the same name but different structure and unordered sequences.
\todo[inline]{Definovat skratku XSD a co to je element type.}

@@

\section{Discovering XML Keys and Foreign Keys in Queries}
This method is described in paper \cite{Necasky:2009:DXK:1529282.1529414}. It tries to improve automatic XML schema inference by discovering keys and foreign keys from a set of XQuery queries. Just the queries are utilized in inference, no XML data are used. The output of this method is a set of keys and foreign keys that can be captured using XML Schema \textbf{key}, \textbf{keyref} \todo{aj unique?} constructs.

@@

\subsubsection{Join patterns}
For a certain join, the decision for one of the cases (O1) and (O2) is made by the form of the join. The query is searched for so-called \emph{join patters}. These are \texttt{for} \emph{join pattern} and \texttt{let} \emph{join pattern} and they look as follows (the first is \texttt{for} \emph{join pattern}, the second is \texttt{let} \emph{join pattern}):

@@

\todo[inline]{Problém je, že tady ste v podstatě opsal ten článek. To je špatně. Analýza ex. přístupů by měla podat přehled toho, co se dnes v dané oblasti umí. Každý přístup by měl být popsán zhruba stejným stylem, stejně podrobně a s jednotným značením. Tj. ne zkopírovat různé odstavce z různých článků, z něčeho 20 řádků a z něčeho 6 stran. To není analýza ale plagiátorství.}

@@

\todo[inline]{Tady by se hodila nějaká srovnávací tabulka metod z různách pohledů (metoda, vstupy, výstupy). Dále pak kapitola na téma co dnešní metody neumí a čím se tedy v práci budeme zbývat. Tj. Nějaká návaznost k další kapitole.}

### 2011-09-08 doc/theses/mikula/analysis_of_xquery.tex
Master thesis: Corrections.

\section{Structure of XML documents}
Most of queries can be exploited to obtain some information about a structure of respective XML documents. The structure of XML documents captures elements from these documents along with their names, attributes and their organization. What the outermost elements in these documents are, which elements can be contained within a certain element, whether they are optional or mandatory, etc.

@@

Additional path expressions \texttt{/bib/book/title}, \texttt{//author/name} indicate that element \texttt{book} also contains element \texttt{title} and element \texttt{author} contains element \texttt{name}. The latter one uses also descendant axis.

@@

However, statements of this kind are necessary for the XML schema inference, their obtaining from queries is not significant due to the following reason. These statements could be determined directly from the XML documents and it could be easily done in a more convenient way. Queries may not cover the whole relevant content of the documents. For example some element may not be queried at all, therefore they may not be mentioned in any query. In addition, these statements do not express any obligation of occurrence of elements and attributes or possible multiple occurrence of elements. We cannot be sure that queries target nodes actually presented in the XML documents. Although query \texttt{/bib/book/author} indicates that element \texttt{author} is contained in element \texttt{book}, the query is valid whether this is true or not. In contrast, even basic methods of XML documents analysis do not have these inadequacies.

@@

@@

\subsection{Join of Recursive Data}
By the term 'recursive data' are meant XML elements that somehow reference items from the same set. Example of a query that operates upon such data follows.

@@

Apparently, element \texttt{part} can contain attributes \texttt{partid} and \texttt{partof}. Elements with unspecified attribute \texttt{partof} are at the top of the recursive hierarchy while, in elements with this attribute specified it makes a reference to an element with attribute \texttt{partid} of the same value.

>>>>

\section{Structure of XML documents}
Most of queries can be exploited to obtain some information about a structure of respective XML documents. The structure of XML documents captures elements from these documents along with their names, attributes and their organization. What the \todo{Co to znamená? Root element?}outermost elements in these documents are, which elements can be contained within a certain element, whether they are optional or mandatory, etc.

@@

Additional path expressions \texttt{/bib/book/title}, \texttt{//author/name} indicate that element \texttt{book} also contains element \texttt{title} and element \texttt{author} contains element \texttt{name}. The latter one uses also descendant axis. \todo{A k čemu je tato informace při odvozování?}

@@

However, statements of this kind are necessary for the XML schema inference, their obtaining from queries is not significant due to the following reason. These statements could be determined directly from the XML documents and it could be easily done in a more convenient way. Queries may not cover the whole relevant content of the documents. For example some element may not be queried at all, therefore they may not be mentioned in any query \todo[inline]{Tady je ale několik případů - chtělo by popsat.
1) Element není zapsaný v dotazu, ale dostanu ho výsledku - např. rok anrození autora, ptám-li se na autory.
2) Element není zapsaný v dotazu, ale procházím ho při vyhodnocování -  např. to //autor
3) Element je v části dokumentu, která se dotazu vlbec netýká.}. In addition, these statements do not express any obligation of occurrence of elements and attributes or possible multiple occurrence of elements \todo{Tak toto je asi taky diskutabilní, např. // by mohlo naznačovat více výskytů.}. We cannot be sure that queries target nodes actually presented in the XML documents. Although query \texttt{/bib/book/author} indicates that element \texttt{author} is contained in element \texttt{book}, the query is valid whether this is true or not. In contrast, even basic methods of XML schema inference that utilize XML documents do not have these inadequacies.

@@

\todo[inline]{Tady by to chtělo příklad. nebo to budeme řešit dál v navrženém algoritmu a toto je pouze diskuse případů?}

@@

\subsection{Join of Recursive Data}
By the term ``recursive data'' are meant XML elements that somehow reference items from the same set. \todo[inline]{Tohle je velmi nepřesné. Tady asi myslíte reference, ale rekurzivní element je obecně element, kteý obsahuje sám sebe - např. kapitola má kapitoly.} Example of a query that operates upon such data follows.

@@

Apparently, element \texttt{part} can contain attributes \texttt{partid} and \texttt{partof}. Elements with unspecified attribute \texttt{partof} are at the top of the recursive hierarchy while, in elements with this attribute specified it makes a reference to an element with attribute \texttt{partid} of the same value. \todo{Tahle věta je nějaká divná.}
